Matching Bullets

### 2015-11-29 imaging-paper.Rnw
attempt at including perfect scenario in the paper ... need more discussion

>>>>

\hh{We can use the Hamby study to run all unkowns against the known bullets. When things go perfectly, they look like in Figure~\ref{fig:hamby-perfect}.}

\begin{figure}
\begin{subfigure}[t]{.49\textwidth}
\caption{Maximal number of CMS between Bullet land and all of the 120 other (known) lands. For two lands the number of maximum CMS is high. }
<<cms, echo=FALSE, fig.width=5, fig.height=3, out.width='\\textwidth'>>=
load("data/unkn17.RData")
cmsdist <- sapply(reslist, function(x) x$maxCMS)

qplot(cmsdist, geom="bar") + theme_bw() + xlab("Number of CMS")
@
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}
\caption{Overlaid lines of the land of the unknown bullet and the land with the top matching CMS.}
<<top, echo=FALSE, fig.width=5, fig.height=3, out.width='\\textwidth'>>=
res <- reslist[[which.max(cmsdist)]]  
#res <- reslist[[which.max(cmsdist[-which.max(cmsdist)])]]  # number 2

print(ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=miny, xmax=maxy), ymin=-6, ymax=5, fill="grey90", data=res$lines) +
  geom_line(aes(x = y, y = l30, colour = bullet),  data = res$bullets) +
  geom_hline(yintercept = res$threshold) +
  geom_hline(yintercept = - res$threshold) +
  scale_colour_brewer(palette="Set1") +
  theme(legend.position = c(1,1), legend.justification=c(1,1)) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match)))

\caption{Overlaid lines of the land of the unknown bullet and the land with the second top matching CMS.}
<<top2, echo=FALSE, fig.width=5, fig.height=3, out.width='\\textwidth'>>=
#res <- reslist[[which.max(cmsdist)]]  
res <- reslist[[which.max(cmsdist[-which.max(cmsdist)])]]  # number 2

print(ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=miny, xmax=maxy), ymin=-6, ymax=5, fill="grey90", data=res$lines) +
  geom_line(aes(x = y, y = l30, colour = bullet),  data = res$bullets) +
  geom_hline(yintercept = res$threshold) +
  geom_hline(yintercept = - res$threshold) +
  scale_colour_brewer(palette="Set1") +
  theme(legend.position = c(1,1), legend.justification=c(1,1)) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match)))

@
\end{subfigure}
\end{figure}
